\textbf{SPECFEM3D Cartesian}\\ \textbf{User Manual}

### 2017-07-04 doc/USER_MANUAL/05_running_the_solver.tex
clarified the depth definition in doc/USER_MANUAL/manual_SPECFEM3D_Cartesian.pdf

For any particular earthquake, the \texttt{CMTSOLUTION} file that
represents the point source may be obtained directly from the Harvard
Centroid-Moment Tensor (CMT) web page \urlwithparentheses{www.seismology.harvard.edu}.
It looks like the example shown in Fig. \ref{fig:CMTSOLUTION-file}.
\begin{figure}[htp]
\begin{centering}
\includegraphics[width=0.8\textwidth]{figures/Hollywood_CMT.jpg}
\par
\end{centering}
\caption{\texttt{CMTSOLUTION} file based on the
format from the Harvard CMT catalog. \textbf{M} is the moment tensor,
$M_{0}${\small {} }is the seismic moment, and $M_{w}$ is the moment
magnitude.}
\label{fig:CMTSOLUTION-file}
\end{figure}
%
The \texttt{CMTSOLUTION} file should be edited in the following way:
\begin{itemize}
\item Set the latitude or UTM $x$ coordinate, longitude or UTM $y$ coordinate, depth of the source (in km).
\item Set the \texttt{time shift} parameter equal to $0.0$ (the solver
will not run otherwise.) The time shift parameter would simply apply
an overall time shift to the synthetics, something that can be done
in the post-processing (see Section \ref{sec:Process-data-and-syn}).
\item For point-source simulations (see finite sources, page \pageref{To-simulate-a})
we recommend setting the source half-duration parameter \texttt{half
duration} equal to zero, which corresponds to simulating a step source-time
function, i.e., a moment-rate function that is a delta function. If
\texttt{half duration} is not set to zero, the code will use a Gaussian
(i.e., a signal with a shape similar to a `smoothed triangle', as
explained in \citet{KoTr02a} and shown in Fig~\ref{fig:gauss.vs.triangle})
source-time function with half-width \texttt{half duration}. We prefer
to run the solver with \texttt{half duration} set to zero and convolve
the resulting synthetic seismograms in post-processing after the run,
because this way it is easy to use a variety of source-time functions
(see Section \ref{sec:Process-data-and-syn}). \citet{KoTr02a} determined
that the noise generated in the simulation by using a step source
time function may be safely filtered out afterward based upon a convolution
with the desired source time function and/or low-pass filtering. Use
the serial code \texttt{convolve\_source\_timefunction.f90} and the
script \texttt{convolve\_source\_timefunction.csh} for this purpose,
or alternatively use signal-processing software packages such as SAC
\urlwithparentheses{www.llnl.gov/sac}. Type
{\small
\begin{verbatim}
make xconvolve_source_timefunction
\end{verbatim}
}
to compile the code and then set the parameter \texttt{hdur} in \texttt{convolve\_source\_timefunction.csh}
to the desired half-duration.

>>>>

For any particular earthquake, the \texttt{CMTSOLUTION} file that
represents the point source may be obtained directly from the Harvard
Centroid-Moment Tensor (CMT) web page \urlwithparentheses{www.seismology.harvard.edu}.
It looks like the example shown in Fig. \ref{fig:CMTSOLUTION-file}.
\begin{figure}[htp]
\begin{centering}
\includegraphics[width=0.8\textwidth]{figures/Hollywood_CMT.jpg}
\par
\end{centering}
\caption{\texttt{CMTSOLUTION} file based on the
format from the Harvard CMT catalog. \textbf{M} is the moment tensor,
$M_{0}${\small {} }is the seismic moment, and $M_{w}$ is the moment
magnitude.}
\label{fig:CMTSOLUTION-file}
\end{figure}
%
The \texttt{CMTSOLUTION} file should be edited in the following way:
\begin{itemize}
\item Set the latitude or UTM $x$ coordinate, longitude or UTM $y$ coordinate, depth of the source (in km). Remark: In principle in the international CMTSOLUTION format in geophysics
the depth is given in kilometers; however for users in other fields (non-destructive testing, medical imaging, near-surface studies...) who may prefer to give the position of the source (rather than its depth from the surface) we provide an option called USE\_SOURCES\_RECEIVERS\_Z in the Par\_file, and if so that position is read from CMTSOLUTION in meters rather than kilometers (and again, it is then the true position in the mesh, not the depth). When option USE\_SOURCES\_RECEIVERS\_Z in the Par\_file is on, this remark applies to the position of the receivers as well.
\item Set the \texttt{time shift} parameter equal to $0.0$ (the solver
will not run otherwise.) The time shift parameter would simply apply
an overall time shift to the synthetics, something that can be done
in the post-processing (see Section \ref{sec:Process-data-and-syn}).
\item For point-source simulations (see finite sources, page \pageref{To-simulate-a})
we recommend setting the source half-duration parameter \texttt{half
duration} equal to zero, which corresponds to simulating a step source-time
function, i.e., a moment-rate function that is a delta function. If
\texttt{half duration} is not set to zero, the code will use a Gaussian
(i.e., a signal with a shape similar to a `smoothed triangle', as
explained in \citet{KoTr02a} and shown in Fig~\ref{fig:gauss.vs.triangle})
source-time function with half-width \texttt{half duration}. We prefer
to run the solver with \texttt{half duration} set to zero and convolve
the resulting synthetic seismograms in post-processing after the run,
because this way it is easy to use a variety of source-time functions
(see Section \ref{sec:Process-data-and-syn}). \citet{KoTr02a} determined
that the noise generated in the simulation by using a step source
time function may be safely filtered out afterward based upon a convolution
with the desired source time function and/or low-pass filtering. Use
the serial code \texttt{convolve\_source\_timefunction.f90} and the
script \texttt{convolve\_source\_timefunction.csh} for this purpose,
or alternatively use signal-processing software packages such as SAC
\urlwithparentheses{www.llnl.gov/sac}. Type
{\small
\begin{verbatim}
make xconvolve_source_timefunction
\end{verbatim}
}
to compile the code and then set the parameter \texttt{hdur} in \texttt{convolve\_source\_timefunction.csh}
to the desired half-duration.
